{\LARGE \textsc{Structural controlability of pollination networks}}\\ {\normalsize Supplementary Information}

### 2016-03-08 paper/supp_info.Rnw
complete methods and update some results

\begin{table}[h]
\centering
\small
<<table n_driver, echo = FALSE, warning = F, message = F, results = "asis">>=
# find n_driver
n_driver <- n_matched %>%
  dplyr::inner_join(meta) %>%
  dplyr::filter(!is.na(inv)) %>%
  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
                n_dr_p = 1 - n_matched / (n_pla + n_pol))

n_driver %>%
  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p) %>%
  dplyr::mutate(site = as.numeric(as.factor(site)),
                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
                n_dr_p = paste0(round(n_dr_p * 100), "%")) %>%
  dplyr::rename_("invaded" = "inv",
                 "No. plants" = "n_pla",
                 "No. polinators" = "n_pol",
                 "No. driver spp." = "n_dr",
                 "prop. driver spp." = "n_dr_p") %>%
  dplyr::arrange(site) %>%
  kable(align = "c", booktabs = T, 
        linesep = c("", "\\addlinespace"))
@
\caption{\label{table:n_driver} Minimum number and proportion of driver species necessary to control the full pollination network}
\end{table}

@@

@
\caption{\label{table:corr_driver} Spearman correlation coefficients of the number of driver species necessary to control the full pollination network.}
\end{table}

@@

\begin{figure}[h]
\centering
<<matrix representation, echo = FALSE, warning = F, message = F, fig.height=4, fig.width=5.5>>=
p <- net[meta$net_name[meta$study == "ballantyne" & meta$count != "binary"]] %>%
	plyr::ldply(function(x) {
		data.frame(vname = igraph::E(net[[1]]) %>% attr("vnames"), 
							weight = igraph::E(x)$weight)
	}) %>%
	dplyr::rename_("net_name" = ".id") %>%
	dplyr::mutate(net_name_f = factor(net_name,  
																		levels = c( 'bal_eff','bal_vis','bal_imp'),
																		labels = c("a) Deposition", "b) Visitation", "c) Importance")), 
	              pla = stringr::str_split_fixed(vname, "\\|", 2)[, 1],
	              pol = stringr::str_split_fixed(vname, "\\|", 2)[, 2]) %>%
  plyr::dlply("net_name_f", function(x){
    p1 <- x %>%
      ggplot(aes(x = pol, y = pla)) +
      geom_tile(aes(fill = weight, width = 0.9, height = 0.9)) + 
      coord_fixed() +
      scale_fill_gradient(low = "#f0f0f0", high = "#525252") +
      ylab("plants") +
      xlab("pollinators") + 
      fer_theme +
      theme(axis.text = element_blank(), 
            axis.ticks = element_blank(), 
            legend.position = "right", 
            legend.title = element_blank(), 
            plot.margin = grid::unit(c(6,0,2,5), "mm"),
            panel.grid = element_blank(),
            legend.key.width = grid::unit(4, "mm"),
            legend.key.height = grid::unit(4, "mm"))
    p2 <- x %>% ggplot(aes(x = weight)) +
      scale_x_log10() +
      stat_density(aes(y =..density..), geom = "line") +
      xlab("link weight") + 
      ylab("density") +
      ggtitle(x$net_name_f[1]) +
      fer_theme +
      theme(plot.margin = grid::unit(c(2,2,0,0), "mm"))
    list(p1, p2)
  })

>>>>

\begin{table}[h]
\centering
\small
<<table n_driver, echo = FALSE, warning = F, message = F, results = "asis">>=
# find n_driver
n_driver <- n_matched %>%
  dplyr::full_join(meta) %>% 
  dplyr::filter(!is.na(inv)) %>%
  dplyr::mutate(n_dr = n_pla + n_pol - n_matched,
                n_dr_p = 1 - n_matched / (n_pla + n_pol))

n_driver %>%
  dplyr::select(site, inv, n_pla, n_pol, n_dr, n_dr_p, study) %>%
  dplyr::arrange(study, site) %>%
  dplyr::mutate(site = rep(1:dplyr::n_distinct(site), each = 2),
                inv = plyr::mapvalues(inv, c(TRUE, FALSE), c("yes", "no")),
                n_dr_p = paste0(round(n_dr_p * 100), "%"),
                study = plyr::mapvalues(study, 
                                        c("bartomeus", "lopezaraiza"),
                                        c("Bartomeus et al. (2008)",
                                          "Lopezaraiza-Mikel et al. (2007)"))) %>%
  dplyr::rename_("invaded" = "inv",
                 "No. pla." = "n_pla",
                 "No. pol." = "n_pol",
                 "No. driver spp." = "n_dr",
                 "prop. driver spp." = "n_dr_p",
                 "source" = "study") %>%
  kable(align = "c", booktabs = T, 
        linesep = c("", "\\addlinespace"))
@
\caption{\label{table:n_driver} Properties of the analysed plant-pollinator communities.}
\end{table}

@@

@
\caption{\label{table:corr_driver} Spearman correlation coefficients of the number of driver species necessary to control the full pollination network under the four different assumptions of the direction of control.}
\end{table}

We built a set of three generalised linear models with a logistic error structure to investigate the variables that influence the set of driver species. We found that the proportion of driver species is largely independent of the study site but highly dependent on the ratio of plant to pollinator diveristy (\autoref{table:n_driver_explanatory}).

\begin{table}[h]
\centering
\small
<<table explaining n_driver, echo = FALSE, warning = F, message = F, results = "asis">>=

m_nr <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol) + study, 
          data = n_driver, 
          family = "binomial")
m1 <- glm(cbind(n_dr, n_matched) ~ I(n_pla/n_pol), 
          data = n_driver, 
          family = "binomial")
m2 <- glm(cbind(n_dr, n_matched) ~ study, 
          data = n_driver, 
          family = "binomial")

ms <- MuMIn::model.sel(m_nr, m1, m2)

i <- 1:3 # indices of columns with model terms
response <- "p_d"

res <- as.data.frame(ms)
v <- names(ms)[i]
v[v == "(Intercept)"] <- 1

# create formula-like model names:
mnames <- apply(res[, i], 1, function(x) 
     deparse(MuMIn::simplify.formula(reformulate(v[!is.na(x)], response = response)))) %>%
  sub("study", "s", .) %>%
  sub("I(n_pla/n_pol)", "r_{p/a}", ., fixed = T) %>%
  sub("~", '\\\\sim', .) %>%
  paste0("$", ., "$")

res <- dplyr::rename_(res, "$\\Delta$AIC" = "delta")

cbind(model = mnames, res[, -i]) %>%
  knitr::kable(align = "c", booktabs = T, digits = 2, escape = F, row.names = F, linesep = "")
@
\caption{\label{table:n_driver_explanatory} The proportion of species needed to control the network ($p_d$) is largaly influenced by the ratio of plant to pollinator species richness ($r_{p/a}$) but not the location of the community ($s$).}
\end{table}

@@

\begin{figure}[h]
\centering
<<matrix representation, echo = FALSE, warning = F, message = F, fig.height=4, fig.width=5.5>>=
p <- net[meta$net_name[meta$study == "ballantyne" & meta$count != "binary"]] %>%
	plyr::ldply(function(x) {
		data.frame(vname = igraph::E(x) %>% attr("vnames"), 
							weight = igraph::E(x)$weight)
	}, .inform = T) %>%
	dplyr::rename_("net_name" = ".id") %>%
	dplyr::mutate(net_name_f = factor(net_name,  
																		levels = c( 'bal_eff','bal_vis','bal_imp'),
																		labels = c("a) Deposition", "b) Visitation", "c) Importance")), 
	              pla = stringr::str_split_fixed(vname, "\\|", 2)[, 1],
	              pol = stringr::str_split_fixed(vname, "\\|", 2)[, 2]) %>%
  plyr::dlply("net_name_f", function(x){
    p1 <- x %>%
      ggplot(aes(x = pol, y = pla)) +
      geom_tile(aes(fill = weight, width = 0.9, height = 0.9)) + 
      coord_fixed() +
      scale_fill_gradient(low = "#f0f0f0", high = "#525252") +
      ylab("plants") +
      xlab("pollinators") + 
      fer_theme +
      theme(axis.text = element_blank(), 
            axis.ticks = element_blank(), 
            legend.position = "right", 
            legend.title = element_blank(), 
            plot.margin = grid::unit(c(6,0,2,5), "mm"),
            panel.grid = element_blank(),
            legend.key.width = grid::unit(4, "mm"),
            legend.key.height = grid::unit(4, "mm"))
    p2 <- x %>% ggplot(aes(x = weight)) +
      scale_x_log10() +
      stat_density(aes(y =..density..), geom = "line") +
      xlab("link weight") + 
      ylab("density") +
      ggtitle(x$net_name_f[1]) +
      fer_theme +
      theme(plot.margin = grid::unit(c(2,2,0,0), "mm"))
    list(p1, p2)
  })
